A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-29 paper.tex
merge

\textbf{Dimension 4}
\begin{itemize}
 \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.  This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.  It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.  In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.  In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.  Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.  This twist was studied by Johansen \cite{Johansen}.
 \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.  This twist is equivalent to a mixed version of BF theory with two real directions and one complex holomorphic direction, coupled to a mixed version of a $U$-valued symplectic boson.  This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.  This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
 \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.  This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.  Its equations of motion include the Donaldson-Witten equations.  If the supersymmetry is promoted to $\mc N=4$, then \chris{...twisting homomorphisms} \cite{Lozano, VafaWitten}
 \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
 \item \emph{More general $\mc N=4$ topological twists} \cite{KapustinWitten, ElliottYoo1}
\end{itemize}

\textbf{Dimension 3}
\begin{itemize}
 \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
 \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} \cite{BlauThompson1, KapustinVyas}
 \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} \cite{BlauThompson2, RozanskyWitten} 
\end{itemize}

@@

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6}

 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
 \label{table_of_twists_2d}
\end{table}

@@

\begin{prop}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ and $S_1$ are independent of $\phi$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
\label{prop:integrateoutfield}
\end{prop}

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  Then we define the required perturbative equivalence as follows.  First $F_1(e) = (e, Q_1(e), 0) \in E$.  Then, for $n > 1$, define
\begin{align*}
F_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(F(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
\end{proof}

@@

\begin{prop}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
\label{prop:BRSTdoublet}
\end{prop}

\begin{proof}
Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.  We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining 
\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  Also, by construction, the $F_n$ intertwine the action functionals, since
\begin{align*}
S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
&= S_0(e).
\end{align*}
Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
\end{proof}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
\label{sect:4d2Donaldson}

@@

Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
As in Section \ref{sect:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.

@@

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.  The $R$-symmetry group is $G_R = \Spin(7;\RR)$, acting on $W$ by its (Dirac) spin representation.

>>>>

\textbf{Dimension 4}
\begin{itemize}
 \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.  This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.  It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.  In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.  In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.  Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.  This twist was studied \chris{in the pure case? check} by Johansen \cite{Johansen}.  Including the chiral multiplet, this twist was considered in \cite{ACMV}.
 \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.  This twist is equivalent to a mixed version of BF theory with two real directions and one complex holomorphic direction, coupled to a mixed version of a $U$-valued symplectic boson.  This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.  This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
 \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.  This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.  Its equations of motion include the Donaldson-Witten equations.  If the supersymmetry is promoted to $\mc N=4$, then  \cite{Lozano, VafaWitten}
 \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
 \item \emph{More general $\mc N=4$ topological twists} \cite{KapustinWitten, ElliottYoo1}
\end{itemize}

\textbf{Dimension 3}
\begin{itemize}
 \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
 \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.}
 \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.}
\end{itemize}

@@

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

@@

\begin{prop}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, \omega, S)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ and $S_1$ are independent of $\phi$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
\label{prop:integrateoutfield}
\end{prop}

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  Then we define the required perturbative equivalence as follows.  First $F_1(e) = (e, Q_1(e), 0) \in E$.  Then, for $n > 1$, define
\begin{align*}
F_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(F(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
\end{proof}

@@

%\begin{prop}
%Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
%\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
%where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
%\label{prop:BRSTdoublet}
%\end{prop}

\begin{prop} 
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \left(F \oplus F^! [-1]\right) \oplus \left(F^! \oplus F[-1] \right)
\]
and $\omega$ given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
Suppose further that the action functional
\[
S = S_0 + \int \phi^* \psi - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
\]
satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are local functionals. 
Then, the classical BV theory $(E, \omega, S)$ is equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}$ and $\psi^* = I_{\phi}$ in the original action functional $S$. 
\end{prop}

\begin{proof}
Again, concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ defining 
\[F_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

The maps $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
Also, by construction, the $F_n$ intertwine the action functionals, since
\begin{align*}
S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
&= S'(e).
\end{align*}
The linear term $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
\end{proof}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
\label{sec:4d2Donaldson}

@@

Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
As in Section \ref{sec:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.

@@

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.  The $R$-symmetry group is $G_R = \Spin(7;
RR)$, acting on $W$ by its (Dirac) spin representation.
